Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-10 docs/ms.tex
Update ms.tex

\caption{The figure shows the posterior samples of reduced shear g
in all the 64 patches . The two blues lines indicate the poisition of
true(input) $g_{1}$ and $g_{2}$. The Blue '+' shows the position
of sample mean, while the red '+' shows the result of mean ellipticity
estimator.}
\end{figure}

@@

We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies, and
the true P($\epsilon$) is Beta(2.8,2.8). The step function model is used with the prior prefator $\xi=3$.
The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 .

@@

One limitation of the step function model is that it needs to be \textit{regularized};
this is achieved by assigning a prior PDF for the step heights $\vec{\alpha}$.
We use the form $Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$
when inferring the P($\epsilon$) and $g$. The choice of this functional
form corresponds to the assumption that the true P($\epsilon$) is
smooth, which seems fairly natural. This function has a hyperparameter,
$\xi$, that needs to be set somehow. If $\xi$ is too small, the
inferred P($\epsilon$) will be too noisy, and the accuracy of the
$g$ inference will decrease. Likewise, choosing an $\xi$ that is
too large, the inferred P($\epsilon$) will be too smooth, and the
data will be under-fitted. In principle one could infer $\xi$ form
the data at hand, but in practice we find that we further more need some
prior regularizer on $\xi$ to obtain correct inference. Therefore in this paper 
we just tuned $\xi$ empirically .From various trials, We find
that $\xi$ should be proportional to the mean data number density and can
be approximated by the following empirical formula: 
\begin{equation}
\xi=N<\rho(|\epsilon|)>/256*\frac{Nbin}{10}
\end{equation}
Here $<\rho|\epsilon|>=\int\rho(|\epsilon|)^{2}d(|\epsilon|)$ corresponds
to the average of data number density,and Nbin is the number of bins used 
in step function model.

>>>>

\caption{The figure shows the posterior samples of reduced shear g
in all the 64 patches. The two blues lines indicate the poisition of
true(input) $g_{1}$ and $g_{2}$. The Blue '+' shows the position
of sample mean, while the red '+' shows the result of mean ellipticity
estimator.}
\end{figure}

@@

We calculated the value of $\hat{g}-g^{true}$ of 10,000 data. Each data set has 64 patches and 8$\times$64 galaxies, and
the true(input) P($\epsilon_{0}$) is Beta(2.8,2.8). The step function model is used with the prior prefator $\xi=3$.
The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 .

@@

One limitation of the step function model is that it needs to be \textit{regularized};
this is achieved by assigning a prior PDF for the step heights $\vec{\alpha}$.
We use the form $Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})$
when inferring the P($\epsilon$) and $g$. The choice of this functional
form corresponds to the assumption that the true P($\epsilon$) is
smooth, which seems fairly natural. This function has a hyperparameter,
$\xi$, that needs to be set somehow. If $\xi$ is too small, the
inferred P($\epsilon$) will be too noisy, and the accuracy of the
$g$ inference will decrease. Likewise, choosing an $\xi$ that is
too large, the inferred P($\epsilon$) will be too smooth, and the
data will be under-fitted. In principle one could infer $\xi$ form
the data at hand, but in practice we find that we further more need some
prior regularizer on $\xi$ to obtain correct inference. Therefore in this paper 
we just tuned $\xi$ empirically. From various trials, We find
that $\xi$ should be proportional to the mean data number density and can
be approximated by the following empirical formula: 
\begin{equation}
\xi=N<\rho(|\epsilon|)>/256*\frac{Nbin}{10}
\end{equation}
Here $<\rho|\epsilon|>=\int\rho(|\epsilon|)^{2}d(|\epsilon|)$ corresponds
to the average of data number density, and Nbin is the number of bins used 
in step function model.
